Infra-estrutura de Testes para Implementações de Referência do Standard ECMAScript

### 2022-05-23 paper.tex
first draft of the Evaluation and planning

% printscreens do site 
\begin{figure}[ht]
    \centering
    \includegraphics[width=1\textwidth]{images/website.png}
    \caption{Website for searching the metadata in construction}
    \label{fig:website}
\end{figure}

@@

% Evaluation 
% - Discutimos avaliação das duas componentes do projecto 
% Componente 1 -> sistema para calculo da metadata
% É muito difícil de avaliar porque não há ground truth -> nós não sabemos qual é a versão dos testes
% - vamos seleccionar um conjunto aleatório de testes e analisa-los à mão comparando a versão calculada com a versão que sabemos ser a versão do teste 
% - vamos tb determinar a versão utilizando à data em que o teste foi inserido na Test262 -> pela data sabemos a versão corrente -> vamos olhar particularmente para os testes em que a versão calculada difere da versão da data dos testes 
% -> Atenção que a versão à data do teste não é necessariamente a versão do teste -> mas dá uma indicação
% --> testes analisados manualmente são os testes para os quais há grandes discrepâncias entre a versão à data do teste e a versão calculada para o teste
% Componente 2 -> sistema de visualisacao 
% -- testes unitários para testar as funcionalidades base da aplicação 
% -- end-to-end tests -> testes do front-end 
% Planning -> usar texto equivalente ao Miguel Trigo 
% - Melhoria do sistema de calculo da metadata - 2 meses
% - Conclusão do sistema de visualização - 2 meses
% - Avaliação - 1 mês 
% - Thesis Writing - 2 meses 
% Julho - (Agosto férias) - Novembro

>>>>

% % printscreens do site 
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=1\textwidth]{images/website.png}
%     \caption{Website for searching the metadata in construction}
%     \label{fig:website}
% \end{figure}

@@

% Evaluation 
% - Discutimos avaliação das duas componentes do projecto

% Componente 1 -> sistema para calculo da metadata
% É muito difícil de avaliar porque não há ground truth -> nós não sabemos qual é a versão dos testes
% - vamos seleccionar um conjunto aleatório de testes e analisa-los à mão comparando a versão calculada com a versão que sabemos ser a versão do teste 
% - vamos tb determinar a versão utilizando à data em que o teste foi inserido na Test262 -> pela data sabemos a versão corrente -> vamos olhar particularmente para os testes em que a versão calculada difere da versão da data dos testes 
% -> Atenção que a versão à data do teste não é necessariamente a versão do teste -> mas dá uma indicação
% --> testes analisados manualmente são os testes para os quais há grandes discrepâncias entre a versão à data do teste e a versão calculada para o teste

% Componente 2 -> sistema de visualisacao
% -- testes unitários para testar as funcionalidades base da aplicação 
% -- end-to-end tests -> testes do front-end

% Para 1 --> components a serem testadas
This thesis we will make improvements to the metadata calculation of \texttt{MetaData262 v0} and create a visualization system for it. The metadata improvements are divided into precision and performance. The evaluation of this thesis contributions is described in more detail bellow.

% Para 2 --> Metadata calculation precision  
\paragraph{Evaluation of metadata calculation precision}
The precision of the metadata calculated is very hard to access since the is no ground truth available. For example the versions of the tests are not available. Thus, to evaluate the the metadata calculation we will select a small random group of tests to analyze manually and compare the the version calculated. A second evaluation will be made to the tests that have the biggest difference between the version calculated and the version that was the latest at the time the test was added to \texttt{Test262}. Firstly, we will find the date the test was added to \texttt{Test262} and associate it with the latest \texttt{ECMAScript} version at that time. After, we will select the tests with the biggest discrepancy between the versions. Finally we will preform a manual evaluation to ensure that the right version was calculated. Note that the version discrepancy is merely indicative as more the once tests were detected as missing and subsequently added to complement \texttt{Test262}.

% Para 3 --> Metadata calculation performance
\paragraph{Evaluation of metadata calculation performance}
To evaluate performance improvements made to \texttt{MetaData262 v0} we will compare the time needed to preform the metadata calculation. This must be ran in the same system and with the least concurrent processes running in order to make sure we have better results.

% Para 4 --> visualization system
\paragraph{Evaluation of the visualization system}
The visualization system evaluation will have three types of tests: unit tests, end-to-end tests and load tests. The unit tests will ensure the correctness and reliability of the system. The end-to-end tests will guarantee that the website interface works correctly. Finally, the load tests will allow us to estimate the amount of users that the systems can support.

\subsection{Planning}
\label{sub:planning}

% subsection planning (end)
% Planning -> usar texto equivalente ao Miguel Trigo 
% - Melhoria do sistema de calculo da metadata - 2 meses
% - Conclusão do sistema de visualização - 2 meses
% - Avaliação - 1 mês 
% - Thesis Writing - 2 meses 
% Julho - (Agosto férias) - Novembro

The Plan for this thesis is based on the tasks that need to be preformed in order to accomplish the objectives defined in section \ref{sec:Goals}. Thus, this thesis has 4 main task to accomplish: improving the metadata calculation, concluding the visualization system, Evaluating the results, and writing the thesis. The planning for these tasks is represented in the Gantt diagram in Figure \ref{fig:gantt} and each task is described in more detail afterwards. Note that the month of August has a grey background due to it being a vacations.

% gantt tese
\begin{figure}[ht]
    \centering
    \includegraphics[width=1\textwidth]{images/gantt_thesis.png}
    \caption{Gantt diagram with the thesis plan}
    \label{fig:gantt}
\end{figure}

% gantt tese tempo dividido por mes
\begin{figure}[ht]
    \centering
    \includegraphics[width=1\textwidth]{images/gantt_thesis_month.png}
    \caption{Gantt diagram with the thesis plan}
    \label{fig:gantt_month}
\end{figure}

\paragraph{Improving metadata calculation}
This task consists of improving \texttt{MetaData262 v0} by improving its precision and performance as discussed in section \ref{sec:Design and Methodology}. The precision will be improved with more JS engines and a JS parser that supports more recent versions of the standard. As for the performance, we will parallelize the metadata calculation.

\paragraph{Concluding visualization system}
This task consists of concluding the \texttt{MetaData262 v0} visualization system by adding the possibility to view statistics about the queried tests and improving the system's reliability through preparing it to handle wrong queries.

\paragraph{Evaluation}
This task consists of evaluating the results of the metadata generated. The most prone to error metadata will be checked by hand in order to guarantee the correctness of the results presented.

\paragraph{Writing the thesis}
This last task will consist in a report of the execution of the previous tasks. In the report we will present the results obtained as well as the conclusions reached after finishing this project.
